Radiocarbon measurement of CO~2~ from carbonate minerals using a gas ion source with an open split interface

### 2022-01-11 doc/AMS-15/AMS-15_poster.Rmd
Change to newer data munger and change rds file suffix

```{r cur-time-os, fig.height=7, dev='svg'}
data <- get_hgis_data(here("data/USAMS040121R.txt"), as.Date("2021-04-02")) %>% 
  filter(Pos == 5) %>% 
  mutate(time = cum_acqtime/60,
         co2flow = concCO2(time, r = 244) * 30) #30ul/min

@@

```{r}
# Read raw and reduced data as produced by analyse_carbonates.R
data <- readRDS(here("data_analysed/carb_all.Rdata"))

>>>>

```{r cur-time-os, fig.height=7, dev='svg'}
data <- process_hgis_results(here("data/USAMS040121R.txt"), as.Date("2021-04-02")) %>% 
  filter(pos == 5) %>% 
  mutate(time = cumsum(corr_lt) / 60,
         co2flow = concCO2(time, r = 244) * 30) #30ul/min

@@

```{r}
# Read raw and reduced data as produced by analyse_carbonates.R
data <- readRDS(here("data_analysed/carb_all.rds"))
